Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-17 paper.tex
move license to intro
extending scikit-learn

The \sklearn project \citep{pedregosa2011} is an open source machine learning
library for the Python programming language. The ambition of the project is to
provide efficient and well-established machine learning tools within a
programming environment that is accessible to non-machine learning experts and
reusable in various scientific areas. The project is not a novel domain-specific
language, but a library that provides machine learning idioms to a general-
purpose high-level language. Among other things, it includes classical learning
algorithms, model selection tools and preprocessing procedures.

@@

\textcolor{red}{TODO}

\textcolor{red}{Point out that any external estimator can be used as base
estimator thanks to duck typing}\\

@@

Any object that conforms to a small superset of the API
lined out in Section~\ref{sec:core-api},
(in particular, that implements methods \texttt{get\_params}
and \texttt{set\_params} for setting hyperparameters;
refer to the documentation at \url{http://scikit-learn.org} for details)
can be used as a \sklearn estimator
and be ``plugged into'' a pipeline, grid search or other meta-estimator
To define such objects, a user can either derive a new class
from \texttt{sklearn.base.BaseEstimator},
or define the entire class from scratch,
without even an \texttt{import sklearn}
in the relevant program module.
The Python principle of ``duck typing''
is employed to make sure that even instances of a class
that does not derive from any \sklearn class can be a first-class estimator.

In other places of the library,
in particular in the feature extraction and vectorization code
for text documents,
the toolkit is designed to be extensible.
Here, the estimators provide ``hooks'' for user-defined code:
objects or functions that provide a specific API
can be given as arguments at vectorizer construction time.
\sklearn code then calls into this code
to obtain the desired behavior.
Again, such user code can be kept agnostic
of the \sklearn class hierarchy,
operating on standard Python objects such as strings instead.

The design principle here is that user code
should not be tied to \sklearn,
which is a \textit{library}, not a \textit{framework}.
This principle avoids a variant of the well-known problem
with object-oriented design,
which is that users wanting a ``banana'' get
``a gorilla holding the banana and the entire jungle''
(Joe~Armstrong, interviewed by \citealp{seibel2009coders}:213):
a program that is not reusable with another machine learning toolkit
(or other solution to the problem at hand),
because it is intimately tied to \sklearn.

@@

The project is distributed under the simplified BSD license, encouraging
its use in both academic and commercial settings.

>>>>

The \sklearn project \citep{pedregosa2011} is an open source machine learning
library for the Python programming language. The ambition of the project is to
provide efficient and well-established machine learning tools within a
programming environment that is accessible to non-machine learning experts and
reusable in various scientific areas. The project is not a novel domain-specific
language, but a library that provides machine learning idioms to a general-
purpose high-level language. Among other things, it includes classical learning
algorithms, model selection tools and preprocessing procedures. The project is
distributed under the simplified BSD license, encouraging its use in both
academic and commercial settings.

@@

\textcolor{red}{TODO: Point out that any external estimator can be used as base
estimator thanks to duck typing}

@@

To ease code reuse, simplify implementation and skip the introduction of
superfluous classes, the principle of \textit{duck typing} is exploited all
throughout the codebase. This technique allows both for extensibility and
flexibility: as long as an estimator follows our API and conventions (as
outlined in Section~\ref{sec:core-api}), then it should be as reusable as any
built-in estimator (e.g., it can plugged within pipelines or grid search
estimators). That is, estimators are specified only by their interface, and not
by inheritance. In particular, this means that external developers can define
their own estimators without being forced to inherit from any internal class of
\sklearn, and rest assured that they can be used as first-class estimators.

In other places of the library, in particular in the feature extraction and
vectorization code for text documents, the toolkit is also designed to be
extensible. Here, estimators provide hooks for user-defined code: objects or
functions that provide a specific API can be given as arguments at vectorizer
construction time. The library then calls into this code to obtain the desired
behavior. Again, such external user code can be kept agnostic of the \sklearn
class hierarchy and operates, for example, on standard Python objects such as
strings instead.

Our rule of thumb is that user code should not be tied to \sklearn -- which is a
\textit{library}, and not a \textit{framework}. This principle indeed avoids a
well-known problem with object-oriented design, which is that users wanting a
``banana'' should not get ``a gorilla holding the banana and the entire jungle''
(Joe~Armstrong, interviewed by \citealp{seibel2009coders}). That is, programs
using \sklearn should be easily reusable with other machine learning toolkits or
in other contexts, because they don't need to be intimately tied to it.

@@
